\ifdefined\build\else\input{head}\fi 

\begin{center}
\textbf{Acknowledgments}
\end{center}

They say having more than one PhD supervisors can be complicated. This was certainly not the case in my PhD. I was very fortunate to have such an understanding and supportive team of supervisors. Their multidisciplinary guidance and support proved invaluable. Rustam Stolkin, Nick Hawes, Kimrom Shapiro; I am very grateful, thank you! Rustam and Nick were always there for me and provided me with trust and freedom on how to manage my time, ideas, and plans. This freedom was one of the most important factors contributing to this thesis. Kim and the people of the Visual Experience Lab made me feel always welcome in their lab meetings. Without the discussions and insights coming from those meetings on how to conduct experiments with human participants, this thesis would have been impossible. 

Next, I would like to thank the dstl technical partner Timothy Harrison for believing in this project and for being very helpful towards overcoming the strict dstl procedures. I would also like to thank Jeremy Baxter for been in the supervision team for the first year of this project.

I am also thankful to Michael Mistry and Russell Beale for all the useful discussions and constructive feedback they provided me during my thesis group meetings. Moreover, I am thankful to the IRlab and ERL members for providing me with feedback on my work. In particular to Chie Takahasi for the long discussions on the human factors aspects of my experiments.

I wish to acknowledge the help provided by the co-authors of my (our) papers. Goda Bieksaite, Jess Kerlin, and Andrew Clouter your help was much appreciated.

Special thanks to my parents, family, and friends. Their support in so many levels during those 4 years was priceless.

Lastly, shout out to all the people who participated in my experiments. They truly made the process of finding volunteers and running the experiments, a breeze. 

This research was supported by the British Ministry of Defence and the UK Defence Science and Technology Laboratory, under their PhD bursary scheme, contract no. DSTLX-1000074621.

\ifdefined\build\else\input{tail}\fi
